iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-24 manuscript/main.tex
author list is full. Todo: dagger or similar for equal contribution

\title{\textit{F1000Research} Article Template}
\titlenote{The title should be detailed enough for someone to know whether the article would be of interest to them, but also concise. Please ensure the broadness and claims within the title are appropriate to the content of the article itself.}
\author[1]{Author Name1}
\author[2]{Author Name2}
\affil[1]{Address of author1}
\affil[2]{Address of author2}

>>>>

\title{iSEE: Interactive SummarizedExperiment Explorer}
\titlenote{The title should be detailed enough for someone to know whether the article would be of interest to them, but also concise. Please ensure the broadness and claims within the title are appropriate to the content of the article itself.}
\author[1]{Kevin Rue-Albrecht}
\author[2,3]{Federico Marini}
\author[4]{Charlotte Soneson}
\author[5]{Aaron T. L. Lun}

\affil[1]{Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom}
\affil[2]{Center for Thrombosis and Hemostasis (CTH), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[3]{Institute for Medical Biostatistics, Epidemiology and Informatics, University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[4]{University of Zurich and SIB Swiss Institute of Bioinformatics, Zurich, Switzerland}
\affil[5]{Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}

% TODO: $^{^\dagger}$These authors contributed equally.}
